---
title: "Polygenic Scores for Complex Traits Predict Multiple Informant Reported Bullying Victimisation: Findings from the Avon Longitudinal Study of Children and Adolescence"
author: "Emma Francis"
date: "`r Sys.Date()`"
output: github_document
always_allow_html: true
---
 
```{r setup, include = FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, ERROR=FALSE}
```

### Overview

##### Polygenic Scores for Complex Traits Predict Multiple Informant Reported Bullying Victimisation

-   1.1 Load packages, read in data
-   1.2 Create teacher and parent subsets
-   1.3 Descriptives and mean victimisation scores by informants and age
-   1.4 Pearson Correlation Matrix of Phenotypes and PGS
-   1.5 Figure: Heatmap of the Included Phenotypes and PGS
-   1.6 Bivariate Regression Models
-   1.7 Figure: Bivariate Associations for PGS by Informants
-   1.8 Multi-PGS in Teacher Subset
-   1.9 Single-PGS in Teacher Subset
-   2.0 Multi-PGS in Parent Subset
-   2.1 Single-PGS in Parent Subset

##### 1.1 Load packages, read in data

```{r}

library(foreign) # load the foreign package
#library(plyr) # load plyr before dplyr to avoid conflict
library(dplyr) 
library(psych)
library(tidyverse)
library(finalfit)
library(lavaan)
library(weights)
library(Hmisc)

complete_data <- read.table("/Users/emma/Desktop/complete_data_02oct2023", header=T, check.names = FALSE) # Other users change path 
head(complete_data)
dim(complete_data)
```

##### 1.2 Create subsets #####
```{r}
##### Main model #####

# Check overlap of variables for main model
complete_data[c("LD_Pred_MDD_std","teacher_sumscale", "BFIS_total_mean", "parent_sumscale")] %>% missing_pattern 

# Conditions need to satisfy in order to be included in the model, include genetic data and at least one phenotype:
# PGS & TR, no PR or SR
# PGS & PR, no TR or SR
# PGS & SR, no TR or PR
# PGS & TR  &  PR, no SR
# PGS & TR & SR, no PR
# PGS & PR & SR, no TR
# PGS & TR & PR & SR

main_model <- subset(complete_data, 
  !is.na(LD_Pred_MDD_std) & !is.na(teacher_sumscale) & is.na(parent_sumscale) & is.na(BFIS_total_mean) # PGS & TR, no PR or SR
   |!is.na(LD_Pred_MDD_std) & !is.na(parent_sumscale) & is.na(teacher_sumscale) & is.na(BFIS_total_mean) # PGS & PR, no TR or SR
  |!is.na(LD_Pred_MDD_std) & !is.na(BFIS_total_mean) & is.na(teacher_sumscale) & is.na(parent_sumscale) # PGS & SR, no TR or PR
   |!is.na(LD_Pred_MDD_std) & !is.na(teacher_sumscale) & !is.na(parent_sumscale) & is.na(BFIS_total_mean) # PGS & TR  &  PR, no SR
|!is.na(LD_Pred_MDD_std) & !is.na(teacher_sumscale) & !is.na(BFIS_total_mean) & is.na(parent_sumscale) # PGS & TR & SR, no PR
  |!is.na(LD_Pred_MDD_std) & !is.na(parent_sumscale) & !is.na(BFIS_total_mean) & is.na(teacher_sumscale) # PGS & PR & SR, no TR
  |!is.na(LD_Pred_MDD_std) & !is.na(teacher_sumscale) & !is.na(parent_sumscale) & !is.na(BFIS_total_mean)) # PGS & TR & PR & SR

dim(main_model) # 8319  148

# Check overlap of variables for main model
main_model[c("LD_Pred_MDD_std","teacher_sumscale", "BFIS_total_mean", "parent_sumscale")] %>% missing_pattern 

##### Not included in Main model #####
# For supplementary analysis comparing included versus non included

#Conditions non included participants satisfy:
# PGS & no TR, no PR, no SR
# no PGS & TR & no SR, no PR
# no PGS & PR & no SR, no TR
# no PGS & SR & no PR, no TR
# no PGS & SR & PR, no TR
# no PGS & no SR & no PR, no TR
# no PGS & no SR & PR, TR
# no PGS & SR & no PR, TR
# no PGS & SR &  PR, TR

excl_main_model <- subset(complete_data, 
  !is.na(LD_Pred_MDD_std) & is.na(teacher_sumscale) & is.na(parent_sumscale) & is.na(BFIS_total_mean) # PGS & no TR, no PR, no SR
   |is.na(LD_Pred_MDD_std) & is.na(parent_sumscale) & !is.na(teacher_sumscale) & is.na(BFIS_total_mean) # no PGS & TR & no SR, no PR
  |is.na(LD_Pred_MDD_std) & is.na(BFIS_total_mean) & is.na(teacher_sumscale) & !is.na(parent_sumscale) # no PGS & PR & no SR, no TR
   |is.na(LD_Pred_MDD_std) & is.na(teacher_sumscale) & is.na(parent_sumscale) & !is.na(BFIS_total_mean) # no PGS & SR & no PR, no TR
|is.na(LD_Pred_MDD_std) & is.na(teacher_sumscale) & !is.na(BFIS_total_mean) & !is.na(parent_sumscale) # no PGS & SR & PR, no TR
  |is.na(LD_Pred_MDD_std) & is.na(parent_sumscale) & is.na(BFIS_total_mean) & is.na(teacher_sumscale) # no PGS & no SR & no PR, no TR
  |is.na(LD_Pred_MDD_std) & !is.na(teacher_sumscale) & !is.na(parent_sumscale) & is.na(BFIS_total_mean) # no PGS & no SR & PR, TR
  |is.na(LD_Pred_MDD_std) & !is.na(teacher_sumscale) & is.na(parent_sumscale) & !is.na(BFIS_total_mean) # no PGS & SR & no PR, TR
  |is.na(LD_Pred_MDD_std) & !is.na(teacher_sumscale) & !is.na(parent_sumscale) & !is.na(BFIS_total_mean)) # no PGS & SR &  PR, TR

dim(excl_main_model) # 7450  148
# Check overlap of variables for main model
excl_main_model[c("LD_Pred_MDD_std","teacher_sumscale", "BFIS_total_mean", "parent_sumscale")] %>% missing_pattern 

# For supplementary material need teacher overlap and parent overlap
##### Teacher model  #####
teacher_model <- subset(complete_data, !is.na(teacher_sumscale) & !is.na(LD_Pred_MDD_std) 
  | !is.na(BFIS_total_mean) & !is.na(LD_Pred_MDD))

# Check overlap: Teacher model 
complete_data[c("LD_Pred_MDD_std","teacher_sumscale", "BFIS_total_mean", "parent_sumscale")] %>% missing_pattern # should only be those with  PGS, and either self-report or parent-report or more

dim(teacher_model) #  8110  148

##### Parent model #####
parent_model <- subset(complete_data, !is.na(parent_sumscale) & !is.na(LD_Pred_MDD_std) 
  | !is.na(BFIS_total_mean) & !is.na(LD_Pred_MDD_std)
   | !is.na(parent_sumscale) & !is.na(LD_Pred_MDD_std))

head(parent_model)
# Check overlap: Parent model 
parent_model[c("LD_Pred_MDD_std","parent_sumscale", "BFIS_total_mean")] %>% missing_pattern # should only be those with PGS, and either self-report or parent-report or more

dim(parent_model) # 7441  148
```

##### 1.3 Descriptives and mean victimisation scores by informants and age

```{r}
##### Descriptives, included ppts=main_model, not included ppts=excl_main_model

# Sex
prop.table(table(main_model$sex))*100  #1=male, 2=female
table(main_model$sex, useNA = "always") # to view missing

prop.table(table(excl_main_model$sex))*100  #1=male, 2=female
table(excl_main_model$sex, useNA = "always") # to view missing

# Age of mother birth (included)
describe(main_model$age_mother_birth)
mean(main_model$age_mother_birth, na.rm = TRUE) # 28.86128
sd(main_model$age_mother_birth, na.rm = TRUE) # 4.577145
range(main_model$age_mother_birth, na.rm = TRUE) # 15-45
# Age of mother birth (not included)
describe(excl_main_model$age_mother_birth)
mean(excl_main_model$age_mother_birth, na.rm = TRUE) # 
sd(excl_main_model$age_mother_birth, na.rm = TRUE) # 
range(excl_main_model$age_mother_birth, na.rm = TRUE) # 

# Maternal Social Class (included)
#obtained at 32 week gestation
#Social class was defined using the UK Registrar General’s occupational coding (SOC 90):
#Elias, P. (1995) 'Social Class and the Standard Occupational Classification', in D. Rose (1995).
#(1) Professional etc occupations
#II Managerial and Technical occupations
#III Skilled occupations
# (N) non-manual
#(M) manual 
# IV Partly-skilled occupations
# V Unskilled occupation
table(main_model$social_class) # 65 = military
describe(main_model$social_class) # number who reported, n=6403

# Maternal Social Class (not included)
table(excl_main_model$social_class) # 65 = military
describe(excl_main_model$social_class) # number who reported, n=7450
#amend the below for each cat
#(122/7450)*100  #proportions

# Maternal Education variables (included)
#obtained at 32 week gestation

# Degree
table(main_model$gest_degree, useNA="always") #1=yes, 2=no, NA=772
describe(main_model$gest_degree) # number who reported, n=7547

# A-level
table(main_model$gest_Alevel, useNA="always") #1=yes, 2=no, NA=772 
describe(main_model$gest_Alevel) # number who reported, n=7547

# O-level
table(main_model$gest_Olevel, useNA="always") #1=yes, 2=no, NA=772
describe(main_model$gest_Olevel) # number who reported, n=7547

# CSE
table(main_model$gest_CSE, useNA="always") #1=yes, 2=no, NA=772
describe(main_model$gest_CSE) # number who reported, n=7547

# No qualification
table(main_model$gest_noqual, useNA="always") #1=yes, 2=no, NA=752
describe(main_model$gest_noqual) # number who reported, n=7547
#(285/7547)*100  #proportions

# Maternal Education variables (not included)
# Degree
table(excl_main_model$gest_degree, useNA="always") #1=yes, 2=no, NA=2333
describe(excl_main_model$gest_degree) # number who reported, n=5117

# A-level
table(excl_main_model$gest_Alevel, useNA="always") #1=yes, 2=no, NA=2333 
describe(excl_main_model$gest_Alevel) # number who reported, n=5117

# O-level
table(excl_main_model$gest_Olevel, useNA="always") #1=yes, 2=no, NA=2333
describe(excl_main_model$gest_Olevel) # number who reported, n=5117

# CSE
table(excl_main_model$gest_CSE, useNA="always") #1=yes, 2=no, NA=2333
describe(excl_main_model$gest_CSE) # number who reported, n=5117

# No qualification
table(excl_main_model$gest_noqual, useNA="always") #1=yes, 2=no, NA=2333
describe(excl_main_model$gest_noqual) # number who reported, n=5117

# percentage female included versus not included
describe(main_model$sex==2) # report TRUE n=4082, 0.492*100
describe(excl_main_model$sex==2) # report TRUE n=3316, 0.484*100

##### Mean victimisation for sum scales by informants #####
##### Teacher composite score included #####
describe(main_model$teacher_sumscale) #n=6258
mean(main_model$teacher_sumscale, na.rm = TRUE) # 2.287152
sd(main_model$teacher_sumscale, na.rm = TRUE) # 0.7435178
range(main_model$teacher_sumscale, na.rm = TRUE) # 2-6

##### Teacher composite score not included #####
describe(excl_main_model$teacher_sumscale) #n=3741
mean(excl_main_model$teacher_sumscale, na.rm = TRUE) # 2.339749
sd(excl_main_model$teacher_sumscale, na.rm = TRUE) # 0.7435178
range(excl_main_model$teacher_sumscale, na.rm = TRUE) # 2-6
#Percent female
table(excl_main_model$teacher_sumscale, excl_main_model$sex==2) # tally the true column
# FALSE TRUE
#  2  1508 1550
#  3   138  101
#  4   207  152
# 5    10    5
#  6    36   31
#1550+101+152+5+31+1508+138+207+10+36  #3738, total sample
#1550+101+152+5+31 # 1839, report female
#1839/3738*100  #females reported in sample


##### Self-report composite score included  #####
describe(main_model$BFIS_total_mean) #n=6730
mean(main_model$BFIS_total_mean, na.rm = TRUE) # -0.01170297
sd(main_model$BFIS_total_mean, na.rm = TRUE) # 0.984831
range(main_model$BFIS_total_mean, na.rm = TRUE) # -0.9132616  6.9867758
#Percent female
table(main_model$BFIS_total_mean<7, main_model$sex==2) # tally the true column, <7 will capture all reporting
#      FALSE TRUE
#TRUE  3354 3363 # 3363, report female
#3354+3363 #6717, total
#3363/6717*100  #females reported in sample

##### Self-report composite score not included  #####
describe(excl_main_model$BFIS_total_mean) #n=1703
mean(excl_main_model$BFIS_total_mean, na.rm = TRUE) # 0.05
sd(excl_main_model$BFIS_total_mean, na.rm = TRUE) # 1.05
range(excl_main_model$BFIS_total_mean, na.rm = TRUE) # -0.9132616  6.9867758
#Percent female
table(excl_main_model$BFIS_total_mean<7, excl_main_model$sex==2) # tally the true column, <7 will capture all reporting
#      FALSE TRUE
#TRUE  841  860 # 860, report female
#841+860 #1701, total
#860/1701*100  #females reported in sample

##### Parent composite score included  #####
describe(main_model$parent_sumscale) #n=6668
mean(parent_model$parent_sumscale, na.rm = TRUE) # 2.506599
sd(parent_model$parent_sumscale, na.rm = TRUE) # 0.8977005
range(parent_model$parent_sumscale, na.rm = TRUE) # 2-6
#Percent female
table(parent_model$parent_sumscale, parent_model$sex==2) # tally the true column
#     FALSE TRUE
#2    2298 2407
#3    454  427
#4    481  373
#5    72   51
#6    63   42
#3300+2298+454+481+72+63 #6668, total sample
#2407+427+373+51+42 # 3300, report female
#3300/6668*100  #females reported in sample

##### Parent composite score not included  #####
describe(excl_main_model$parent_sumscale) #n=2140
mean(excl_main_model$parent_sumscale, na.rm = TRUE) # 2.53
sd(excl_main_model$parent_sumscale, na.rm = TRUE) # 0.9467776
range(excl_main_model$parent_sumscale, na.rm = TRUE) # 2-6
# Percent female
table(excl_main_model$parent_sumscale, excl_main_model$sex==2) # tally the true column
#     FALSE TRUE
#2   772  755
#  3   105  121
#  4   166  139
#  5    22   13
#  6    26   21
#755+121+139+13+21+772+105+166+166+22+26  #2306, total sample
#755+121+139+13+21 # 1049, report female
#1049/2306*100  #females reported in sample

# Compare included versus not included (mean comparison for cont var. chi squared for binary)
complete_data$inclusion[complete_data$cidB3496 %in% main_model$cidB3496] <- 1
complete_data$inclusion[is.na(complete_data$inclusion)] <- 0
table(complete_data$inclusion)
class(complete_data$inclusion)

# Comparing age of mother at birth 
t.test(complete_data$age_mother_birth, complete_data$inclusion, alternative = "two.sided", var.equal = FALSE) # Welch Two Sample t-test

# Compare female included
chisq.test(complete_data$sex==2, complete_data$inclusion)

# Comparing social class
str(complete_data$social_class) # check type of variable
# ordinal
complete_data <- complete_data %>%
  dplyr::mutate(social_class_ord = as.factor(social_class) %>% as.ordered())
str(complete_data$social_class_ord)
levels(complete_data$social_class_ord)
# Chosen chisquared for consistency - similar findings for all approaches
#wilcox.test(social_class ~ inclusion, data=complete_data) 
chisq.test(complete_data$social_class_ord, complete_data$inclusion)

# Comparing education variables
# compare degree across included versus not included 
chisq.test(complete_data$gest_degree, complete_data$inclusion)
# compare a-level across included versus not included 
chisq.test(complete_data$gest_Alevel, complete_data$inclusion)
# compare o-level across included versus not included
chisq.test(complete_data$gest_Olevel, complete_data$inclusion)
# compare cse across included versus not included
chisq.test(complete_data$gest_CSE, complete_data$inclusion)
# compare no qualifactions across included versus not included
chisq.test(complete_data$gest_noqual, complete_data$inclusion)

# Comparing composite scores
# compare self-report composite score across included versus not included (Welch Two Sample t-test)
t.test(complete_data$BFIS_total_mean ~ complete_data$inclusion, alternative = "two.sided", var.equal = FALSE)

# compare parent-report composite score across included versus not included
t.test(complete_data$parent_sumscale ~ complete_data$inclusion, alternative = "two.sided", var.equal = FALSE)
# compare teacher-report composite score across included versus not included
t.test(complete_data$teacher_sumscale ~ complete_data$inclusion, alternative = "two.sided", var.equal = FALSE)
```

##### 1.4 Pearson Correlation Matrix of Phenotypes and PGS 
```{r}
complete_data_subset <- main_model[,c("parent_sumscale", "teacher_sumscale", "BFIS_total_mean", "LD_Pred_ADHD", "LD_Pred_MDD", "LD_Pred_EA", "LD_Pred_BMI", "LD_Pred_ANX", "LD_Pred_NEURO", "LD_Pred_SZ")] # only phenotype and polygenic scores in the correlation table
wtd.cor(complete_data_subset) # reports correlation with all digits
cor<-corr.test(complete_data_subset) # correlations between variables (2digits)
print(cor, short=FALSE) # report unadjusted confidence intervals
rcorr(as.matrix(complete_data_subset)) # reports p values

# self-report and teacher-report
cor.test(complete_data_subset$teacher_sumscale, complete_data_subset$BFIS_total_mean, method='pearson') 
# parent and self-report
cor.test(complete_data_subset$parent_sumscale, complete_data_subset$BFIS_total_mean, method='pearson') 
```

##### 1.5 Figure: Heatmap of the Included Phenotypes and PGS ##### 
```{r}
# Rename variable names in subset 
complete_data_rename <- dplyr::rename(complete_data_subset, SR = BFIS_total_mean,
                      PR = parent_sumscale,TR = teacher_sumscale, 
                      EA = LD_Pred_EA, MDD = LD_Pred_MDD,ADHD = LD_Pred_ADHD, 
                      BMI = LD_Pred_BMI, NEURO = LD_Pred_NEURO,
                      ANX = LD_Pred_ANX, SZ = LD_Pred_SZ)
head(complete_data_rename)

# Plot
library(corrplot)
X <-cor(complete_data_rename, use='p')
          type = 'upper'
          col=colorRampPalette(c("blue","white","red"))(20) 
          order = c("original") # default 
          tl.col = "black"
          tl.srt=45 # colour of text and angle of x labels

colnames(X) <- c("Parent-report", "Teacher-report", "Self-report", "ADHD", "Depression", "Education Attainment", "Body Mass Index","Anxiety", "Neuroticism", "Schizophrenia")
rownames(X) <- c("Parent-report", "Teacher-report", "Self-report", "ADHD", "Depression", "Education Attainment", "Body Mass Index","Anxiety", "Neuroticism", "Schizophrenia")
# Edit figure 
#corrplot(cor(X, use='p'), 
 #         type = 'upper',col=colorRampPalette(c("blue","white","red"))(20), 
#          order = c("original"), # default 
#          tl.col = "black",tl.srt=45) # colour of text and angle of x labels


# Edit figure 
corrplot(X, 
          type = 'upper',col=colorRampPalette(c("blue","white","red"))(20), 
          order = c("original"), # default 
          tl.col = "black",tl.srt=55) # colour of text and angle of x labels

# Rename variable names in subset in preparation for bivariate association analysis and figure 2 - use the standardised pgs
complete_data_figure2<- dplyr::rename(complete_data, SR = BFIS_total_mean,
                      PR = parent_sumscale,TR = teacher_sumscale, 
                      EA = LD_Pred_EA_std, MDD = LD_Pred_MDD_std, ADHD = LD_Pred_ADHD_std, 
                      BMI = LD_Pred_BMI_std, NEURO = LD_Pred_NEURO_std,
                      ANX = LD_Pred_ANX_std, SZ = LD_Pred_SZ_std, AN = LD_Pred_AN_std)

head(complete_data_figure2)
```

##### 1.6 Bivariate Regression Models 
```{r}
##### Self-report #####

#PGS-MDD
self_mdd <- '
            # regressions
            SR ~ MDD + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_self <- sem(self_mdd, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_self, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge1 <- parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge1 <- merge1[1:1, ]
merge1

#PGS-SZ
self_sz <- '
            # regressions
            SR ~ SZ + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_self <- sem(self_sz, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_self, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge2 <- parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge2 <- merge2[1:1, ]
merge2

#PGS-ADHD
self_adhd <- '
            # regressions
            SR ~ ADHD + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_self <- sem(self_adhd, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_self, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge3 <- parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge3 <- merge3[1:1, ]
merge3

#PGS-Anxiety
self_anx <- '
            # regressions
            SR ~ ANX + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_self <- sem(self_anx, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_self, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge4 <- parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge4 <- merge4[1:1, ]
merge4

#PGS-Neuroticism
self_neuro <- '
            # regressions
            SR ~ NEURO + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_self <- sem(self_neuro, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_self, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge5 <- parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge5 <- merge5[1:1, ]
merge5

#PGS-BMI
self_bmi <- '
            # regressions
            SR ~  BMI  + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_self <- sem(self_bmi, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_self, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge6 <- parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge6 <- merge6[1:1, ]
merge6

#PGS-Education attainment
self_ea <- '
            # regressions
            SR ~ EA + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_self <- sem(self_ea, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_self, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge7 <- parameterEstimates(fit_self, ci = TRUE, level = 0.95)
merge7 <- merge7[1:1, ]
merge7

merged_data <- bind_rows(merge1, merge2, merge3, merge4, merge5, merge6, merge7)
merged_data # check

##### Parent-report #####
#PGS-MDD
parent_mdd <- '
                # regressions
                PR ~ MDD  + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                '
fit_parent <- sem(parent_mdd, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_parent, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge8 <- parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge8 <- merge8[1:1, ] # by default head only shows first 6 col, we need first 7
merge8

#PGS-SZ
parent_sz <- '
            # regressions
            PR ~ SZ + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_parent <- sem(parent_sz, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_parent, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge9 <- parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge9 <- merge9[1:1, ]
merge9

#PGS-ADHD
parent_adhd <- '
            # regressions
            PR ~ ADHD + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_parent <- sem(parent_adhd, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_parent, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge10 <- parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge10 <- merge10[1:1, ]
merge10

#PGS-Anxiety
parent_anx <- '
            # regressions
            PR ~ ANX + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_parent <- sem(parent_anx, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_parent, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge11 <- parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge11 <- merge11[1:1, ]
merge11

#PGS-Neuroticism
parent_neuro <- '
            # regressions
            PR ~ NEURO + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_parent <- sem(parent_neuro, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_parent, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge12 <- parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge12 <- merge12[1:1, ]
merge12

#PGS-BMI
parent_bmi <- '
            # regressions
            PR ~ BMI + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_parent <- sem(parent_bmi, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_parent, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge13 <- parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge13 <- merge13[1:1, ]
merge13

#PGS-Education attainment
parent_ea <- '
            # regressions
            PR ~ EA + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_parent <- sem(parent_ea, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_parent, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge14 <- parameterEstimates(fit_parent, ci = TRUE, level = 0.95)
merge14 <- merge14[1:1, ]
merge14

##### Teacher-report #####
#PGS-MDD
teacher_mdd <- '
                # regressions
                TR ~ MDD + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_teacher <- sem(teacher_mdd, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x=FALSE) # added .x as without this does not impute all pred and outcome, may need to add fixed.x = FALSE
summary(fit_teacher, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge15 <- parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge15 <- merge15[1:1, ] 
merge15 

#PGS-SZ
teacher_sz <- '
            # regressions
            TR ~ SZ + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_teacher <- sem(teacher_sz, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_teacher, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge16 <- parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge16 <- merge16[1:1, ]
merge16

#PGS-ADHD
teacher_adhd <- '
            # regressions
            TR ~ ADHD + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_teacher <- sem(teacher_adhd, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_teacher, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge17 <- parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge17 <- merge17[1:1, ]
merge17

#PGS-Anxiety
teacher_anx <- '
            # regressions
            TR ~ ANX + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_teacher <- sem(teacher_anx, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_teacher, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge18 <- parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge18 <- merge18[1:1, ]
merge18

#PGS-Neuroticism
teacher_neuro <- '
            # regressions
            TR ~ NEURO + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_teacher <- sem(teacher_neuro, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_teacher, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge19 <- parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge19 <- merge19[1:1, ]
merge19

#PGS-BMI
teacher_bmi <- '
            # regressions
            TR ~ BMI + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_teacher <- sem(teacher_bmi, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_teacher, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge20 <- parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge20 <- merge20[1:1, ]
merge20

#PGS-Education attainment
teacher_ea <- '
            # regressions
            TR ~ EA + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
            '
fit_teacher <- sem(teacher_ea, data=complete_data_figure2, estimator = "ML", missing="FIML.x", fixed.x = FALSE) # added .x as without this does not impute all pred and outcome
summary(fit_teacher, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge21 <- parameterEstimates(fit_teacher, ci = TRUE, level = 0.95)
merge21 <- merge21[1:1, ]
merge21

# Merge the data together for figure: https://dplyr.tidyverse.org/reference/bind.html
merged_data <- bind_rows(merge1, merge2, merge3, merge4, merge5, merge6, merge7, merge8, merge9,
                          merge10, merge11, merge12, merge13, merge14, merge15, merge16, merge17,
                          merge18, merge19, merge20, merge21) 

merged_data
```

##### 1.7 Figure: Bivariate Associations for PGS by Informants
```{r}
merged_data # View

merged_data2 <- merged_data %>%
                 dplyr::rename("Informant" = "lhs", "PGS" = "rhs", "Estimate" = "est")
merged_data2 # View  

merged_data2$Informant <- rep(c("SR", "PR", "TR"), each = 7)
merged_data2$star <- ifelse(merged_data2$pvalue < 0.05, "*", "")

# Plot regression by informant
p <- ggplot(merged_data2, aes(group = Informant)) +
  geom_vline(xintercept = 0, linetype = 2) + #facet_grid(Class~Role, scales = "free_y") +
  geom_errorbarh(data = merged_data2,
                 mapping = aes(y = PGS, x = Estimate, xmin = ci.lower, xmax = ci.upper, 
                               color = Informant),
                 height = 0.6,
                 size = 1, 
                 position = position_dodge(0.7)) + 
  geom_point(data = merged_data2, 
             mapping = aes(y = PGS, x = Estimate, color = Informant), 
             size = 3, shape = 19,
             position = position_dodge(0.7)) +
      geom_text(aes(x = Estimate, y = PGS, label = star), size = 6, position = position_dodge(0.7)) +
   labs(x = "Estimate")

p # view

# Edit so colour in gigure is similar to earlier plotted figure
# Solution for using colour twice: https://stackoverflow.com/questions/50733237/how-can-colour-be-added-manually-in-ggplot-and-legend-labels-renamed-in-the-same
p + scale_color_manual(
            values = c("blue", "orchid", "red"), #change colour
            labels = c("Parent-report", "Self-report", "Teacher-report")) + # change legend names
scale_y_discrete(labels = c("SZ"="Schizophrenia", "MDD"="Depression", "NEURO"="Neuroticism", 
                  "EA"="Education Attainment", "BMI"="Body Mass Index", "ANX"="Anxiety")) # edit y axis labels
```
##### 1.8 Multi-PGS for Main Model 
```{r}
model1 <- model1 <- '
                    # regressions
                    BFIS_total_mean ~ teacher_sumscale + parent_sumscale + LD_Pred_MDD_std + LD_Pred_SZ_std + LD_Pred_ADHD_std + LD_Pred_ANX_std + LD_Pred_NEURO_std + LD_Pred_EA_std + LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std +  pc10_std
                    
                    teacher_sumscale ~ LD_Pred_MDD_std + LD_Pred_SZ_std + LD_Pred_ADHD_std + LD_Pred_ANX_std + LD_Pred_NEURO_std + LD_Pred_EA_std +  LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    parent_sumscale ~ LD_Pred_MDD_std + LD_Pred_SZ_std + LD_Pred_ADHD_std + LD_Pred_ANX_std + LD_Pred_NEURO_std + LD_Pred_EA_std + LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    LD_Pred_MDD_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_SZ_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_ADHD_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_ANX_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_NEURO_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_EA_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_BMI_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    #correlations
                    parent_sumscale~~teacher_sumscale
                    LD_Pred_MDD_std~~LD_Pred_SZ_std
                    LD_Pred_MDD_std~~LD_Pred_ADHD_std
                    LD_Pred_MDD_std~~LD_Pred_ANX_std
                    LD_Pred_MDD_std~~LD_Pred_NEURO_std
                    LD_Pred_MDD_std~~LD_Pred_EA_std
                    LD_Pred_MDD_std~~LD_Pred_BMI_std
                    
                    LD_Pred_SZ_std~~LD_Pred_ADHD_std
                    LD_Pred_SZ_std~~LD_Pred_ANX_std
                    LD_Pred_SZ_std~~LD_Pred_NEURO_std
                    LD_Pred_SZ_std~~LD_Pred_EA_std
                    LD_Pred_SZ_std~~LD_Pred_BMI_std
                    
                    LD_Pred_ADHD_std~~LD_Pred_ANX_std
                    LD_Pred_ADHD_std~~LD_Pred_NEURO_std
                    LD_Pred_ADHD_std~~LD_Pred_EA_std
                    LD_Pred_ADHD_std~~LD_Pred_BMI_std
                    
                    LD_Pred_ANX_std~~LD_Pred_NEURO_std
                    LD_Pred_ANX_std~~LD_Pred_EA_std
                    LD_Pred_ANX_std~~LD_Pred_BMI_std

                    LD_Pred_NEURO_std~~LD_Pred_EA_std
                    LD_Pred_NEURO_std~~LD_Pred_BMI_std
                    
                    LD_Pred_EA_std~~LD_Pred_BMI_std
                    
                    ' 
fit_mod <- sem(model1, data=main_model, estimator = "ML", missing="FIML.x") 
# added .x as without this does not impute all pred and outcome
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95) # save variables
```
##### 1.9 Single-PGS in Main model - MDD
```{r}
##### Main model - Single PGS-MDD #####
model1_mdd <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + teacher_sumscale + LD_Pred_MDD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_MDD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    teacher_sumscale ~ LD_Pred_MDD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    LD_Pred_MDD_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(model1_mdd, data=main_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

# Extract the beta estimates for PGS MDD on self-report, parent-report and teacher-report
```
##### 1.9 Single-PGS in Main model - SZ 
```{r}
model1_sz <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + teacher_sumscale + LD_Pred_SZ_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_SZ_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    teacher_sumscale ~ LD_Pred_SZ_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    LD_Pred_SZ_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(model1_sz, data=main_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

# Extract the beta estimates for PGS SZ on self-report, parent-report and teacher-report
```
##### 1.9 Single-PGS in Main model - ADHD
```{r}
model1_adhd <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + teacher_sumscale + LD_Pred_ADHD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_ADHD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    teacher_sumscale ~ LD_Pred_ADHD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    LD_Pred_ADHD_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(model1_adhd, data=main_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)
# Extract the beta estimates for PGS ADHD on self-report, parent-report and teacher-report
```
##### 1.9 Single-PGS in Main model - Anxiey
```{r}
model1_anx <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + teacher_sumscale + LD_Pred_ANX_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_ANX_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    teacher_sumscale ~ LD_Pred_ANX_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    LD_Pred_ANX_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(model1_anx, data=main_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)
# Extract the beta estimates for PGS Anxiety on self-report, parent-report and teacher-report
```
##### 1.9 Single-PGS in Main model - Neuro
```{r}
model1_neuro <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + teacher_sumscale + LD_Pred_NEURO_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_NEURO_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    teacher_sumscale ~ LD_Pred_NEURO_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    LD_Pred_NEURO_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(model1_neuro, data=main_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)
# Extract the beta estimates for PGS Neuroticism on self-report, parent-report and teacher-report
```
##### 1.9 Single-PGS in Main model - Educational attainment
```{r}
model1_ea <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + teacher_sumscale + LD_Pred_EA_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_EA_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    teacher_sumscale ~ LD_Pred_EA_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    LD_Pred_EA_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(model1_ea, data=main_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)
# Extract the beta estimates for PGS Education Attainment on self-report, parent-report and teacher-report
```
##### 1.9 Single-PGS in Main model - BMI
```{r}
model1_bmi <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + teacher_sumscale + LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    teacher_sumscale ~ LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    LD_Pred_BMI_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(model1_bmi, data=main_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)
# Extract the beta estimates for PGS BMI on self-report, parent-report and teacher-report
```
##### 1.8 Supplementary Table Multi-PGS in Teacher Subset 
```{r}
teacher_multipgs<- model1 <- '
                    # regressions
                    BFIS_total_mean ~ teacher_sumscale + LD_Pred_MDD_std + LD_Pred_SZ_std + LD_Pred_ADHD_std + LD_Pred_ANX_std + LD_Pred_NEURO_std + LD_Pred_EA_std + LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    teacher_sumscale ~ LD_Pred_MDD_std + LD_Pred_SZ_std + LD_Pred_ADHD_std + LD_Pred_ANX_std + LD_Pred_NEURO_std + LD_Pred_EA_std + LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    LD_Pred_MDD_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_SZ_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_ADHD_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_ANX_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_NEURO_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_EA_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_BMI_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std

                    #correlations
                    LD_Pred_MDD_std~~LD_Pred_SZ_std
                    LD_Pred_MDD_std~~LD_Pred_ADHD_std
                    LD_Pred_MDD_std~~LD_Pred_ANX_std
                    LD_Pred_MDD_std~~LD_Pred_NEURO_std
                    LD_Pred_MDD_std~~LD_Pred_EA_std
                    LD_Pred_MDD_std~~LD_Pred_BMI_std
                    
                    LD_Pred_SZ_std~~LD_Pred_ADHD_std
                    LD_Pred_SZ_std~~LD_Pred_ANX_std
                    LD_Pred_SZ_std~~LD_Pred_NEURO_std
                    LD_Pred_SZ_std~~LD_Pred_EA_std
                    LD_Pred_SZ_std~~LD_Pred_BMI_std
                    
                    LD_Pred_ADHD_std~~LD_Pred_ANX_std
                    LD_Pred_ADHD_std~~LD_Pred_NEURO_std
                    LD_Pred_ADHD_std~~LD_Pred_EA_std
                    LD_Pred_ADHD_std~~LD_Pred_BMI_std
                    
                    LD_Pred_ANX_std~~LD_Pred_NEURO_std
                    LD_Pred_ANX_std~~LD_Pred_EA_std
                    LD_Pred_ANX_std~~LD_Pred_BMI_std

                    LD_Pred_NEURO_std~~LD_Pred_EA_std
                    LD_Pred_NEURO_std~~LD_Pred_BMI_std
                    
                    LD_Pred_EA_std~~LD_Pred_BMI_std
                    
                    ' 
fit_mod <- sem(teacher_multipgs, data=teacher_model, estimator = "ML", missing="FIML.x") # added .x as without this does not impute all pred and outcome
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95) # save variables

# Report the relationship between PGS and self-report, teacher-report, and between teacher and self-report
```
##### 1.9 Supplementary Table Single-PGS in Teacher Subset
```{r}
##### Single PGS-MDD in Teacher Subset #####
teacher_mdd <- '
                    # regressions
                    BFIS_total_mean ~ teacher_sumscale + LD_Pred_MDD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    teacher_sumscale ~ LD_Pred_MDD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_MDD_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(teacher_mdd, data=teacher_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

##### Single PGS-SZ in Teacher Subset #####
teacher_sz <- '
                    # regressions
                    BFIS_total_mean ~ teacher_sumscale + LD_Pred_SZ_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    teacher_sumscale ~ LD_Pred_SZ_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_SZ_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(teacher_sz, data=teacher_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

##### Single PGS-ADHD in Teacher Subset #####
teacher_adhd <- '
                    # regressions
                    BFIS_total_mean ~ teacher_sumscale + LD_Pred_ADHD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    teacher_sumscale ~ LD_Pred_ADHD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_ADHD_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(teacher_adhd, data=teacher_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

##### Single PGS-Anxiety in Teacher Subset #####
teacher_anx <- '
                    # regressions
                    BFIS_total_mean ~ teacher_sumscale + LD_Pred_ANX_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    teacher_sumscale ~ LD_Pred_ANX_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_ANX_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(teacher_anx, data=teacher_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

##### Single PGS-Neuro in Teacher Subset #####
teacher_neuro <- '
                    # regressions
                    BFIS_total_mean ~ teacher_sumscale + LD_Pred_NEURO_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    teacher_sumscale ~ LD_Pred_NEURO_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_NEURO_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(teacher_neuro, data=teacher_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

##### Single PGS-EA in Teacher Subset #####
teacher_ea <- '
                    # regressions
                    BFIS_total_mean ~ teacher_sumscale + LD_Pred_EA_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    teacher_sumscale ~ LD_Pred_EA_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_EA_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(teacher_ea, data=teacher_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

##### Single PGS-BMI in Teacher Subset #####
teacher_bmi <- '
                    # regressions
                    BFIS_total_mean ~ teacher_sumscale + LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    teacher_sumscale ~ LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_BMI_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(teacher_bmi, data=teacher_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)
```
##### 2.0 Supplementary Table Multi-PGS in Parent Subset
```{r}
parent_multipgs <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + LD_Pred_MDD_std + LD_Pred_SZ_std + LD_Pred_ADHD_std + LD_Pred_ANX_std + LD_Pred_NEURO_std + LD_Pred_EA_std + LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_MDD_std + LD_Pred_SZ_std + LD_Pred_ADHD_std + LD_Pred_ANX_std + LD_Pred_NEURO_std + LD_Pred_EA_std + LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    
                    LD_Pred_MDD_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_SZ_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_ADHD_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_ANX_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_NEURO_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_EA_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    LD_Pred_BMI_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std

                    #correlations
                    LD_Pred_MDD_std~~LD_Pred_SZ_std
                    LD_Pred_MDD_std~~LD_Pred_ADHD_std
                    LD_Pred_MDD_std~~LD_Pred_ANX_std
                    LD_Pred_MDD_std~~LD_Pred_NEURO_std
                    LD_Pred_MDD_std~~LD_Pred_EA_std
                    LD_Pred_MDD_std~~LD_Pred_BMI_std
                    
                    LD_Pred_SZ_std~~LD_Pred_ADHD_std
                    LD_Pred_SZ_std~~LD_Pred_ANX_std
                    LD_Pred_SZ_std~~LD_Pred_NEURO_std
                    LD_Pred_SZ_std~~LD_Pred_EA_std
                    LD_Pred_SZ_std~~LD_Pred_BMI_std
                    
                    LD_Pred_ADHD_std~~LD_Pred_ANX_std
                    LD_Pred_ADHD_std~~LD_Pred_NEURO_std
                    LD_Pred_ADHD_std~~LD_Pred_EA_std
                    LD_Pred_ADHD_std~~LD_Pred_BMI_std
                    
                    LD_Pred_ANX_std~~LD_Pred_NEURO_std
                    LD_Pred_ANX_std~~LD_Pred_EA_std
                    LD_Pred_ANX_std~~LD_Pred_BMI_std

                    LD_Pred_NEURO_std~~LD_Pred_EA_std
                    LD_Pred_NEURO_std~~LD_Pred_BMI_std
                    
                    LD_Pred_EA_std~~LD_Pred_BMI_std
                  
                    ' 
fit_mod <- sem(parent_multipgs, data=parent_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

```
##### 2.1 Supplementary Table Single-PGS in Parent Subset ##### 
```{r}
##### Single PGS-MDD in Parent Subset 
parent_mdd <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + LD_Pred_MDD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_MDD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_MDD_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(parent_mdd, data=parent_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

##### Single PGS-SZ in Parent Subset #####
parent_sz <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + LD_Pred_SZ_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_SZ_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_SZ_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(parent_sz, data=parent_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

##### Single PGS-ADHD in Parent Subset #####
parent_adhd <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + LD_Pred_ADHD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_ADHD_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_ADHD_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(parent_adhd, data=parent_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

##### Single PGS-Anxiety in Parent Subset #####
parent_anx <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + LD_Pred_ANX_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_ANX_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_ANX_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(parent_anx, data=parent_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

##### Single PGS-Neuroticism in Parent Subset #####
parent_neuro <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + LD_Pred_NEURO_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_NEURO_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_NEURO_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(parent_neuro, data=parent_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

##### Single PGS-Education attainment in Parent Subset #####
parent_ea <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + LD_Pred_EA_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_EA_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_EA_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(parent_ea, data=parent_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)

##### Single PGS-BMI in Parent Subset #####
parent_bmi <- '
                    # regressions
                    BFIS_total_mean ~ parent_sumscale + LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    parent_sumscale ~ LD_Pred_BMI_std + sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
          
                    LD_Pred_BMI_std ~ sex + SR_age8 + SR_age10 + pc1_std + pc2_std + pc3_std + pc4_std + pc5_std + pc6_std + pc7_std + pc8_std + pc9_std + pc10_std
                    '
fit_mod <- sem(parent_bmi, data=parent_model, estimator = "ML", missing="FIML.x")
summary(fit_mod, fit.measures=TRUE, standardized=TRUE)
parameterEstimates(fit_mod, ci = TRUE, level = 0.95)
```
